Layered Formal Verification of a TCP Stack

### 2021-09-08 SecDev21/paper.tex
Comparison between C & SPARK code

@@

\begin{figure}
\begin{lstlisting}[language=C, basicstyle=\footnotesize\ttfamily, numbers=left,
    numberstyle=\tiny, frame=bottomline, escapeinside={(*@}{@*)}]
// Create a fake incoming segment
TCPheader *segment = malloc(sizeof(TCPheader));
klee_make_symbolic(segment, sizeof(segment), "seg");
klee_assume(segment->flag <= 31);
// Create the socket
Socket *sock = malloc(sizeof(Socket)), oldSock;
klee_make_symbolic(sock, sizeof(sock), "sock");
memcpy(&oldSock, sock, sizeof(Socket));

@@

@@

% I'll try to add comparison between the time taken by the C and the Ada code.

>>>>

\usepackage{multirow}
\usepackage{array}

@@

\begin{figure}
\begin{lstlisting}[language=C, basicstyle=\footnotesize\ttfamily, numbers=left,
    numberstyle=\tiny, frame=bottomline, escapeinside={(*@}{@*)}, numbersep=2pt]
// Create a fake incoming segment
TCPheader *segment = malloc(sizeof(TCPheader));
klee_make_symbolic(segment, sizeof(segment), "seg");
klee_assume(segment->flag <= 31);
// Create the socket
Socket *sock = malloc(sizeof(Socket)), oldSock;
klee_make_symbolic(sock, sizeof(sock), "sock");
memcpy(&oldSock, sock, sizeof(Socket));

@@

\begin{table}[!t]
    \caption{Comparison of the number of ASM instructions between the C and the SPARK implementation}
    \label{table:instr}
    \renewcommand{\arraystretch}{1.3}
    \centering
    \begin{tabular}{lcc}
    \hline
    \multirow{2}{*}{Function}&\multicolumn{2}{c}{Number of ASM instructions} \\
    &C&SPARK\\ \hline
    \spark{TCP_Listen}   & 18                  & 11                   \\
    \spark{TCP_Accept}   & 153                 & 167                  \\
    \spark{TCP_Connect}  & 103                 & 114                  \\
    \spark{TCP_Send}     & 94                  & 124                  \\
    \spark{TCP_Receive}  & 113                 & 153                  \\
    \spark{TCP_Shutdown} & 107                 & 122                  \\
    \spark{TCP_Abort}    & 42                  & 50                   \\ \hline
    \end{tabular}
\end{table}

@@

Comparing the performance of each C and SPARK functions can be random and might not reflect the real time taken by the functions due to the network latency. Instead, we have reproduced in \Cref*{table:instr} the number of ARM assembly instructions of the TCP functions written in C and in SPARK. We observe that the C functions contain less instructions and then the performance of a C code using the TCP functions will be better than the performance of the same code written in SPARK.
